---
title: "Data preparation from Survey Monkey"
author: "Lynn Pallemaerts"
date: "2025-01-07"
output:
  html_document: default
---

# Libraries

```{r}
library(devtools)
devtools::install_github("mattroumaya/surveymonkey")
library(surveymonkey)
library(tidyverse)

source("./Functions/double_header.R")
```

# Input

## Option 1: Connect with Survey monkey

For some reason, this didn't work anymore the second time around. I tried fixing
it and playing around with settings both here as in Survey Monkey, but no
luck... That's why there's a second option.

```{r}
# m5_survey <- surveymonkey::browse_surveys(title = "Identifying data sharing issues regarding camera trap data in Europe",
#                                           oauth_token = sm_oauth_token)
# survey_ID <- c(m5_survey$id[1])
# 
# # Get whole survey
# survey <- surveymonkey::fetch_survey_obj(survey_ID,
#                                          oauth_token = sm_oauth_token)
# survey_df <- surveymonkey::parse_survey(survey,
#                                         oauth_token = sm_oauth_token) %>%
#   surveymonkey::strip_html()
```

## Option 2: read in csv

```{r}
survey_df <- read_csv("./Input/260115_SM_export/CSV/Identifying data sharing issues regarding camera trap data in Europe.csv") %>%
  double_header()
```

# Get question list

```{r}
qs <- read_delim("./Input/question_list.csv",
                 delim = ";")
```

# Basic data exploration

```{r}
# Get number of total respondents
length(unique(survey_df$respondent_id))

# Get number of complete responses
resp <- survey_df %>%
  select(-collector_id)
length(unique(resp$respondent_id))
```

# Make subset for each question

```{r}
for (i in 1:nrow(qs)) {
  name <- qs$code[i]
  question <- qs$question_export[i]
  assign(name, 
         survey_df %>%
           dplyr::select(respondent_id, contains(question)))
}
remove(i, name, question)
```

# Clean individual dataframes

## Q1

```{r}
Q1 <- q1 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  filter(!is.na(response)) %>%
  mutate(question = qs$question[qs$code == "q1"]) %>%
  mutate(nchar = nchar(question)) %>%
  mutate(long_answer = substring(long_answer, nchar + 4)) %>%
  select(respondent_id, question, response) %>%
  arrange(respondent_id) %>%
  write_csv2("./Interim/question1.csv")
remove(q1)
```

## Q2

```{r}
# WATCH OUT FO OTHER PLEASE SPECIFY
Q2 <- q2 %>%
  mutate(question = qs$question[qs$code == "q2"]) %>%
  rename(response = paste0(qs$question_export[qs$code == "q2"],
                           "_response")) %>%
  mutate(response = ifelse(response == "Other, please specify:",
                           NA,
                           response)) %>%
  mutate(response = coalesce(response,
                             what_country_is_your_primary_affiliation_located_in_other_please_specify)) %>%
  select(respondent_id, question, response) %>%
  arrange(respondent_id) %>%
  write_csv2("./Interim/question2.csv")
remove(q2)
```

## Q3

```{r}
# Q3 <- q3 %>%
#   mutate(question = qs$question[qs$code == "q3"]) %>%
#   rename(response = qs$question[qs$code == "q3"]) %>%
#   select(respondent_id, question, response) %>%
#   write_csv2("./Interim/dummy_question3.csv")
# remove(q3)

# This question was removed between dummy and def version
# Dummy Q4 is now def Q3

# WATCH OUT FO OTHER PLEASE SPECIFY
Q3 <- q3 %>%
  mutate(question = qs$question[qs$code == "q3"]) %>%
  rename(response = paste0(qs$question_export[qs$code == "q3"],
                           "_response")) %>%
  mutate(response = ifelse(respondent_id == 118797829762, "Scientific (research institute)", response)) %>%
  select(respondent_id, question, response) %>%
  arrange(respondent_id) %>%
  write_csv2("./Interim/question3.csv")
remove(q3)
```

## Q4

```{r}
Q4 <- q4 %>%
  mutate(question = qs$question[qs$code == "q4"]) %>%
  rename(response = paste0(qs$question_export[qs$code == "q4"], "_response")) %>%
  filter(!is.na(response)) %>% # For the respondents that did not mark administration in Q3
  select(respondent_id, question, response) %>%
  arrange(respondent_id) %>%
  write_csv2("./Interim/question4.csv")
remove(q4)
```

## Q5

```{r}
# WATCH OUT FO OTHER PLEASE SPECIFY
Q5 <- q5 %>%
  mutate(question = qs$question[qs$code == "q5"]) %>%
  rename(response = paste0(qs$question_export[qs$code == "q5"], "_response")) %>%
  select(respondent_id, question, response) %>%
  arrange(respondent_id) %>%
  write_csv2("./Interim/question5.csv")
remove(q5)
```

## Q6

```{r}
Q6 <- q6 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q6"]) %>%
  mutate(long_answer = str_remove(long_answer, "what_are_your_camera_trapping_related_research_questions_")) %>%
  rename(topic = long_answer) %>%
  select(respondent_id, question, topic, response) %>%
  arrange(respondent_id, topic) %>%
  write_csv2("./Interim/question6.csv")
remove(q6)
```

## Q7

```{r}
Q7 <- q7 %>%
  mutate(question = qs$question[qs$code == "q7"]) %>%
  rename(response = paste0(qs$question_export[qs$code == "q7"], "_open_ended_response")) %>%
  filter(!is.na(response)) %>% # for those who didn't fill this in
  select(respondent_id, question, response) %>%
  arrange(respondent_id) %>%
  write_csv2("./Interim/question7.csv")
remove(q7)
```

## Q8

```{r}
Q8 <- q8 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q8"]) %>%
  mutate(long_answer = str_remove(long_answer, "how_important_do_you_rate_the_following_characteristics_of_potential_camera_trap_data_management_tools_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question8.csv")
remove(q8)
```

## Q9

```{r}
Q9 <- q9 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q9"]) %>%
  mutate(long_answer = str_remove(long_answer, "how_desirable_do_you_find_the_inclusion_of_the_following_features_into_data_management_tools_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question9.csv")
remove(q9)
```

## Q10

```{r}
Q10 <- q10 %>%
  mutate(question = qs$question[qs$code == "q10"]) %>%
  rename(response = paste0(qs$question_export[qs$code == "q10"], "_open_ended_response")) %>%
  filter(!is.na(response)) %>% # for those who didn't fill this in
  select(respondent_id, question, response) %>%
  arrange(respondent_id) %>%
  write_csv2("./Interim/question10.csv")
remove(q10)
```

## Q11

```{r}
Q11 <- q11 %>%
  mutate(question = qs$question[qs$code == "q11"]) %>%
  rename(response = paste0(qs$question_export[qs$code == "q11"], "_open_ended_response")) %>%
  filter(!is.na(response))%>% # for those who didn't fill this in
  select(respondent_id, question, response) %>%
  arrange(respondent_id) %>%
  write_csv2("./Interim/question11.csv")
remove(q11)
```

## Q12

```{r}
Q12 <- q12 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q12"]) %>%
  mutate(long_answer = str_remove(long_answer, "for_the_study_species_your_are_willing_to_share_data_about_at_what_geographical_resolution_are_you_willing_to_share_your_data_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question12.csv")
remove(q12)
```

## Q13

```{r}
Q13 <- q13 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q13"]) %>%
  mutate(long_answer = str_remove(long_answer, "for_the_study_species_your_are_willing_to_share_data_about_at_what_temporal_resolution_are_you_willing_to_share_your_data_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question13.csv")
remove(q13)
```

## Q14

```{r}
Q14 <- q14 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q14"]) %>%
  mutate(long_answer = str_remove(long_answer, "for_the_study_species_your_are_willing_to_share_data_about_at_what_frequency_are_you_willing_to_share_your_data_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question14.csv")
remove(q14)
```

## Q15

```{r}
Q15 <- q15 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q15"]) %>%
  mutate(long_answer = str_remove(long_answer, "would_the_following_safeguards_positively_influence_your_willingness_to_share_data_for_the_species_mentioned_in_q11_and_q12_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question15.csv")
remove(q15)
```

## Q16

```{r}
Q16 <- q16 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q16"]) %>%
  mutate(long_answer = str_remove(long_answer, "how_willing_are_you_to_share_data_for_the_following_purposes_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question16.csv")
remove(q16)
```

## Q17

```{r}
Q17 <- q17 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q17"]) %>%
  mutate(long_answer = str_remove(long_answer, "how_much_of_an_issue_do_you_consider_the_following_obstacles_to_be_in_regards_to_sharing_your_camera_trap_data_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question17.csv")
remove(q17)
```

## Q18

```{r}
Q18 <- q18 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q18"]) %>%
  mutate(long_answer = str_remove(long_answer, "what_geographical_resolution_of_camera_trap_data_would_you_like_to_be_shared_with_you_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question18.csv")
remove(q18)
```

## Q19

```{r}
Q19 <- q19 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q19"]) %>%
  mutate(long_answer = str_remove(long_answer, "what_temporal_resolution_of_camera_trap_data_would_you_like_to_be_shared_with_you_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question19.csv")
remove(q19)
```

## Q20

```{r}
Q20 <- q20 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q20"]) %>%
  mutate(long_answer = str_remove(long_answer, "how_valuable_do_you_think_data_from_unstructured_citizen_science_initiatives_projects_e_g_garden_projects_opportunistic_camera_trapping_are_for_the_following_purposes_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question20.csv")
remove(q20)
```

## Q21

```{r}
Q21 <- q21 %>%
  pivot_longer(!respondent_id, names_to = "long_answer", values_to = "response") %>%
  mutate(question = qs$question[qs$code == "q21"]) %>%
  mutate(long_answer = str_remove(long_answer, "how_valuable_do_you_think_data_from_structured_citizen_science_e_g_targeted_camera_trapping_hunter_owned_camera_traps_are_for_the_following_purposes_")) %>%
  rename(charachteristic = long_answer) %>%
  select(respondent_id, question, charachteristic, response) %>%
  arrange(respondent_id, charachteristic) %>%
  write_csv2("./Interim/question21.csv")
remove(q21)
```

## Q22

```{r}
Q22 <- q22 %>%
  mutate(question = qs$question[qs$code == "q22"]) %>%
  rename(response = paste0(qs$question_export[qs$code == "q22"], "_response")) %>%
  select(respondent_id, question, response) %>%
  arrange(respondent_id) %>%
  write_csv2("./Interim/question22.csv")
remove(q22)
```

## Q23

```{r}
Q23 <- q23 %>%
  mutate(question = qs$question[qs$code == "q23"]) %>%
  rename(response = paste0(qs$question_export[qs$code == "q23"], "_response")) %>%
  select(respondent_id, question, response) %>%
  arrange(respondent_id) %>%
  write_csv2("./Interim/question23.csv")
remove(q23)
```

## Q24

```{r}
Q24 <- q24 %>%
  mutate(question = qs$question[qs$code == "q24"]) %>%
  rename(response = paste0(qs$question_export[qs$code == "q24"], "_open_ended_response")) %>%
  select(respondent_id, question, response) %>%
  arrange(respondent_id) %>%
  write_csv2("./Interim/question24.csv")
remove(q24)
```

## Q25-28

```{r}
Q25678 <- q25 %>%
  left_join(q26, by = "respondent_id") %>%
  left_join(q27, by = "respondent_id") %>%
  left_join(q28, by = "respondent_id") %>%
  rename(gender = paste0(qs$question_export[qs$code == "q25"], "_response"),
         age = paste0(qs$question_export[qs$code == "q26"], "_response"),
         degree = paste0(qs$question_export[qs$code == "q27"], "_response"),
         employment = paste0(qs$question_export[qs$code == "q28"], "_response")) %>%
  write_csv2("./Interim/question25678.csv")
remove(q25, q26, q27, q28)
```

