---
title: "Data analysis from Survey Monkey"
output: html_document
date: "2025-03-18"
---

# Libraries

```{r}
library(fistools)
library(ggforce)
library(patchwork)
library(tidyverse)
library(RColorBrewer)
library(rnaturalearth)
library(sf)

conflicted::conflicts_prefer(dplyr::filter)
conflicted::conflicts_prefer(dplyr::summarise)
conflicted::conflicts_prefer(dplyr::mutate)
```
# Labels

```{r}
labels <- read_delim("./Input/labels.csv", 
                     delim = ";", 
                     escape_double = FALSE, 
                     trim_ws = TRUE)

# fix typos
labels <- labels %>% mutate(
  label = str_replace(label, "of.t thedatain", "of the data in"),
  label = str_replace(label, "requesy", "request"),
  label = str_replace(label, "estimatng", "estimating"),
  label = str_replace(label, "eporting", "reporting"))
```

# Question 1: What country/countries are your activities based in? Multiple answers are possible.

```{r}
q1 <- read_delim("./Interim/question1.csv", 
                 delim = ";",
                 escape_double = FALSE, 
                 trim_ws = TRUE)
```

## Cleaning
```{r}
subset(q1, response == "South Africa" | response == "United States, Peru" | response == "Lebanon")

respondents_to_scrap <- c("118788625159", "119022297166", "119029337164")
```


```{r}
q1 %>%
  ggplot() +
  geom_bar(aes(x = fct_infreq(response))) +
  labs(x = "Country of activities",
       y = "Number of responses") +
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1,
                                   vjust = 0.5)) +
  scale_y_continuous(limits = c(0, 25)) +
  annotate("text",
           x = Inf,
           y = Inf,
           label = paste0("n = ",
                          length(unique(q1$respondent_id)),
                          " | m = ",
                          nrow(q1)),
           vjust = 1,
           hjust = 1,
           size = 3.5)
ggsave("./Output/q1.png",
       dpi = 300,
       width = 16,
       height = 10,
       units = c("cm"))
```

```{r}
# 1. Fetch country regional metadata from rnaturalearth
world_metadata <- ne_countries(scale = "medium", returnclass = "sf") %>%
  st_drop_geometry() %>%
  select(name, subregion)

all_regions <- c(
  "Southern Europe", "Western Europe", "Northern Europe", 
  "Eastern Europe",  "Western Asia",   "Southern Africa", "Northern America"
)
region_colors <- setNames(brewer.pal(7, "Dark2"), all_regions)

# 2. Clean survey country names and join regional metadata
q1_grouped <- q1 %>%
  mutate(response = case_when(
    response == "Czechia" ~ "Czech Republic",
    response == "United States, Peru" ~ "United States of America, Peru", 
    TRUE ~ response
  )) %>%
  separate_longer_delim(response, delim = ", ") %>% 
  left_join(world_metadata, by = c("response" = "name")) %>%
  filter(!is.na(subregion))

# 3. Summarize data into regional totals and multi-line country text blocks
q1_summary <- q1_grouped %>%
  group_by(subregion, response) %>%
  summarise(country_n = n(), .groups = "drop") %>%
  arrange(subregion, desc(country_n)) %>% 
  mutate(country_label = paste0(response, " (", country_n, ")")) %>%
  group_by(subregion) %>%
  summarise(
    total_responses = sum(country_n),
    country_stack = paste(country_label, collapse = "\n")
  )

# 4. Generate final plot with staggered text layouts
q1_summary %>%
  ggplot(aes(x = total_responses, y = fct_reorder(subregion, total_responses), 
             fill = subregion, color = subregion)) +
  geom_col(width = 0.4, show.legend = FALSE) + 
  geom_text(aes(label = country_stack), 
            hjust = 0, 
            vjust = 0.5, 
            nudge_x = 2,           
            size = 2.5,            
            lineheight = 0.85,     
            show.legend = FALSE) +  
  labs(x = "Number of responses", 
       y = "Region/ country of activity",
       subtitle = paste0("n = ", length(unique(q1$respondent_id)), 
                         " | m = ", nrow(q1))) +
  scale_x_continuous(limits = c(0, 100)) + 
  scale_fill_manual(values = region_colors) +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"))

# 5. Save output (height = 22cm provides vertical room to prevent text overlap)
ggsave("./Output/q1_regions.png",
       dpi = 300,
       width = 18,       
       height = 22,   
       units = "cm")
```


# Question 2: What country is your primary affiliation located in?

```{r}
q2 <- read_delim("./Interim/question2.csv", 
                 delim = ";",
                 escape_double = FALSE, 
                 trim_ws = TRUE)
```

```{r}
subset(q2, respondent_id %in% respondents_to_scrap)
```

```{r}
q2 %>% count(response) %>% arrange(desc(n))

q2 %>%
  filter(!is.na(response)) %>%
  ggplot() +
  geom_bar(aes(x = fct_infreq(response))) +
  labs(x = "Country of primary affiliation",
       y = "Number of responses") +
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1,
                                   vjust = 0.5)) +
  scale_y_continuous(limits = c(0, 25)) +
  annotate("text",
           x = Inf,
           y = Inf,
           label = paste0("n = ",
                          length(unique(q2$respondent_id[!is.na(q2$response)]))),
           vjust = 1,
           hjust = 1,
           size = 3.5)
ggsave("./Output/q2.png",
       dpi = 300,
       width = 15,
       height = 10,
       units = c("cm"))
```

```{r}
# 2. Clean survey country names and join regional metadata
q2_grouped <- q2 %>%
  mutate(response = case_when(
    response == "Czechia" ~ "Czech Republic",
    response == "United States" ~ "United States of America",
    TRUE ~ response
  )) %>%
  left_join(world_metadata, by = c("response" = "name")) %>%
  filter(!is.na(subregion))

# 3. Summarize data into regional totals and multi-line country text blocks
q2_summary <- q2_grouped %>%
  group_by(subregion, response) %>%
  summarise(country_n = n(), .groups = "drop") %>%
  arrange(subregion, desc(country_n)) %>% 
  mutate(country_label = paste0(response, " (", country_n, ")")) %>%
  group_by(subregion) %>%
  summarise(
    total_responses = sum(country_n),
    country_stack = paste(country_label, collapse = "\n")
  )

# 4. Generate final plot with staggered text layouts
q2_summary %>%
  ggplot(aes(x = total_responses, y = fct_reorder(subregion, total_responses), 
             fill = subregion, color = subregion)) +
  geom_col(width = 0.4, show.legend = FALSE) + 
  geom_text(aes(label = country_stack), 
            hjust = 0, 
            vjust = 0.5, 
            nudge_x = 2,           
            size = 2.5,            
            lineheight = 0.85,     
            show.legend = FALSE) +  
  labs(x = "Number of responses", 
       y = "Region/ country of primary affiliation",
       subtitle = paste0("n = ",
                          length(unique(q2$respondent_id[!is.na(q2$response)])))) +
  scale_x_continuous(limits = c(0, 100)) + 
  scale_fill_manual(values = region_colors) +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"))

# 5. Save output (height = 22cm provides vertical room to prevent text overlap)
ggsave("./Output/q2_regions.png",
       dpi = 300,
       width = 18,       
       height = 18,   
       units = "cm")
```

# Question 3: How would you classify your primary affiliation?

```{r}
q3 <- read_delim("./Interim/question3.csv", 
                 delim = ";",
                 escape_double = FALSE, 
                 trim_ws = TRUE)
```

```{r}
subset(q3, respondent_id %in% respondents_to_scrap)
```

```{r}
q3 %>%
  filter(!is.na(response)) %>%
  mutate(response = case_when(str_detect(response, "Academic") ~ "Academic",
                              str_detect(response, "Scientific") ~ "Scientific",
                              TRUE ~ response)) %>%
  ggplot() +
  geom_bar(aes(x = fct_infreq(response))) +
  labs(x = "Type of primary affiliation",
       y = "Number of responses") +
  scale_y_continuous(limits = c(0, 75),
                     breaks = seq(0, 75, by = 25)) +
  annotate("text",
           x = Inf,
           y = Inf,
           label = paste0("n = ",
                          length(unique(q3$respondent_id[!is.na(q3$response)]))),
           vjust = 1,
           hjust = 1,
           size = 2.5)
ggsave("./Output/q3.png",
       dpi = 300,
       width = 18,
       height = 12,
       units = c("cm"))
```

# Question 5 : What role do you play in camera trapping-related research?

```{r}
q5 <- read_delim("./Interim/question5.csv", 
                 delim = ";",
                 escape_double = FALSE, 
                 trim_ws = TRUE)
```

```{r}
subset(q5, respondent_id %in% respondents_to_scrap)
```

```{r}
q5 %>%
  filter(!is.na(response)) %>%
  mutate(response = case_when(str_detect(response, "user") ~ "User",
                              str_detect(response, "collector") ~ "Collector",
                              TRUE ~ response)) %>%
  ggplot() +
  geom_bar(aes(x = fct_infreq(response))) +
  labs(x = "",
       y = "Number of responses") +
  scale_y_continuous(limits = c(0, 80),
                     breaks = seq(0, 80, by = 20)) +
  annotate("text",
           x = Inf,
           y = Inf,
           label = paste0("n = ",
                          length(unique(q5$respondent_id[!is.na(q5$response)]))),
           vjust = 1,
           hjust = 1,
           size = 2.5)
ggsave("./Output/q5.png",
       dpi = 300,
       width = 18,
       height = 12,
       units = c("cm"))
```

```{r}
# 1. Prepare, count, and explicitly order the data
chart_data <- left_join(q3, q5, by = "respondent_id") %>%
  filter(!is.na(response.x)) %>%
  mutate(
    response.x = case_when(
      str_detect(response.x, "Academic") ~ "Academic",
      str_detect(response.x, "Scientific") ~ "Scientific",
      TRUE ~ response.x
    ),
    response.y = case_when(
      is.na(response.y) ~ "Not reported",
      str_detect(response.y, "user") ~ "User",
      str_detect(response.y, "collector") ~ "Collector",
      TRUE ~ response.y
    )
  ) %>%
  count(response.x, response.y) %>%
  
  # FIX: Calculate GLOBAL totals for the stacks to force a clean, descending order
  group_by(response.y) %>%
  mutate(total_y = sum(n)) %>%
  ungroup() %>%
  mutate(response.y = fct_reorder(response.y, total_y, .desc = FALSE)) %>%
  
  # Calculate totals for the main bars (largest bar on top)
  group_by(response.x) %>%
  mutate(total_x = sum(n)) %>%
  ungroup() %>%
  mutate(response.x = fct_reorder(response.x, total_x))

# 2. Generate the plot
chart_data %>%
  ggplot(aes(x = n, y = response.x, fill = response.y)) +
  geom_col(width = 0.5) +
  
  # Numbers sit perfectly centered in their respective colored segments
  geom_text(aes(label = n), 
            position = position_stack(vjust = 0.5), 
            color = "white", 
            fontface = "bold", 
            size = 3) +
  
  labs(x = "Number of responses",
       y = "Type of primary affiliation",
       fill = "Role",
       subtitle = paste0("n = ", length(unique(q3$respondent_id[!is.na(q3$response)])))) +
  scale_x_continuous(limits = c(0, 75), breaks = seq(0, 75, by = 25)) +
  scale_fill_brewer(palette = "Dark2", direction = -1) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"))

# 3. Save output
ggsave("./Output/q3_q5_combined.png",
       dpi = 300,
       width = 18,
       height = 12,
       units = "cm")
```


# Question 6: What are your camera trapping-related research questions?

```{r}
# 1. Read and process data
q6 <- read_delim("./Interim/question6.csv", 
                 delim = ";", 
                 escape_double = FALSE, 
                 col_types = cols(respondent_id = col_double()), 
                 trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and sort by decreasing agreement (smallest pci2 at the top)
q6_pci %>%
  # 1. Map fill and color to the continuous mean score
  ggplot(aes(y0 = y, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) + 
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  
  # 2. Let geom_circle inherit the aesthetics (removed hardcoded fill/color)
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q6_pci$y, labels = q6_pci$label) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q6$score),
                     labels = unique(q6$response)) +
  
  # 3. Apply a professional, muted diverging color palette (Red to Blue)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  
  # 4. Hide the gradient legend to keep the focus entirely on the data
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q6$respondent_id[!is.na(q6$response)])))) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

# 4. Save output
ggsave("./Output/q6_pci.png",
       dpi = 300,
       width = 12,
       height = 16,
       units = "cm")
```

# Question 8: How important do you rate the following characteristics of potential camera trap data management tools?

```{r}
# 1. Read and process data
q8 <- read_delim("./Interim/question8.csv", 
                 delim = ";", 
                 escape_double = FALSE, 
                 trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and sort by Mean Score for a diagonal flow
q8_pci <- q8 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
  arrange(meanAnswer) %>%
  mutate(y = row_number())

q8_pci <- q8_pci %>% mutate(label = str_wrap(label, width = 30))

# 3. Generate the plot
q8_pci %>%
  ggplot(aes(y0 = y, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q8_pci$y, labels = q8_pci$label) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q8$score),
                     labels = unique(q8$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q8$respondent_id[!is.na(q8$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# 4. Save output
ggsave("./Output/q8_pci.png",
       dpi = 300,
       width = 16,
       height = 18,
       units = "cm")
```

# Question 9: How desirable do you find the inclusion of the following features into data management tools?

```{r}
# 1. Read and process data
q9 <- read_delim("./Interim/question9.csv", 
                 delim = ";", 
                 escape_double = FALSE, 
                 trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and sort by Mean Score for a diagonal flow
q9_pci <- q9 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
  arrange(meanAnswer) %>%
  mutate(y = row_number())

# 3. Generate the plot
q9_pci %>%
  ggplot(aes(y0 = y, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q9_pci$y, labels = q9_pci$label) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q9$score),
                     labels = unique(q9$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q9$respondent_id[!is.na(q9$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# 4. Save output
ggsave("./Output/q9_pci.png",
       dpi = 300,
       width = 12,
       height = 10,
       units = "cm")
```

# Question 12: For the study species your are willing to share data about, at what geographical resolution are you willing to share your data?

```{r}
# 1. Read and process data
q12 <- read_delim("./Interim/question12.csv", 
                  delim = ";", 
                  escape_double = FALSE, 
                  trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and sort by Mean Score for a diagonal flow
q12_pci <- q12 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
    mutate(ord = case_when(str_detect(label, "National") ~ 7,
                         str_detect(label, "Regional") ~ 6,
                         str_detect(label, "Municipality") ~ 5,
                         str_detect(label, "Study") ~ 4,
                         str_detect(label, "Grid") ~ 3,
                         str_detect(label, "Generalised") ~ 2,
                         str_detect(label, "Exact") ~ 1
                         )
           ) %>%
  # Arranging ensures y-axis breaks and text labels line up perfectly
  arrange(ord)

# 3. Generate the plot
pl12 <- q12_pci %>%
  ggplot(aes(y0 = ord, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  coord_fixed() +
  scale_y_continuous(breaks = q12_pci$ord, labels = q12_pci$label) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q12$score),
                     labels = unique(q12$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q12$respondent_id[!is.na(q12$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# Display the plot object
pl12

# 4. Save output
ggsave("./Output/q12_pci.png",
       dpi = 300,
       width = 16,
       height = 14,
       units = "cm")
```

# Question 13: For the study species your are willing to share data about, at what temporal resolution are you willing to share your data?

```{r}
# 1. Read and process data
q13 <- read_delim("./Interim/question13.csv", 
                  delim = ";", 
                  escape_double = FALSE, 
                  trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and apply your custom chronological sorting sequence
q13_pci <- q13 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
  mutate(ord = case_when(str_detect(label, "Exact") ~ 1,
                         str_detect(label, "Daily") ~ 2,
                         str_detect(label, "Weekly") ~ 3,
                         str_detect(label, "Monthly") ~ 4,
                         str_detect(label, "Annual") ~ 5)) %>%
  # Arranging ensures y-axis breaks and text labels line up perfectly
  arrange(ord) 

# 3. Generate the plot
pl13 <- q13_pci %>%
  ggplot(aes(y0 = ord, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q13_pci$ord, labels = q13_pci$label, limits = c(0.8, 5.5)) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q13$score),
                     labels = unique(q13$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "Frequency / Horizon",
       subtitle = paste0("n = ", length(unique(q13$respondent_id[!is.na(q13$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# Display the plot object
pl13

# 4. Save output
ggsave("./Output/q13_pci.png",
       dpi = 300,
       width = 16,
       height = 12,
       units = "cm")
```

# Question 14: For the study species your are willing to share data about, at what frequency are you willing to share your data?

```{r}
# 1. Read and process data
q14 <- read_delim("./Interim/question14.csv", 
                  delim = ";", 
                  escape_double = FALSE, 
                  trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and sort by Mean Score for a diagonal flow
q14_pci <- q14 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
  arrange(meanAnswer) %>%
  mutate(y = row_number())

q14_pci <- q14_pci %>% mutate(label = str_wrap(label, width = 30))

# 3. Generate the plot
pl14 <- q14_pci %>%
  ggplot(aes(y0 = y, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q14_pci$y, labels = q14_pci$label) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q14$score),
                     labels = unique(q14$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q14$respondent_id[!is.na(q14$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# Display the plot object
pl14

# 4. Save output
ggsave("./Output/q14_pci.png",
       dpi = 300,
       width = 16,
       height = 14,
       units = "cm")
```

# Question 15: Would the following safeguards positively influence your willingness to share data, for the species mentioned in Q11 and Q12?

```{r}
# 1. Read and process data
q15 <- read_delim("./Interim/question15.csv", 
                 delim = ";", 
                 escape_double = FALSE, 
                 trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and sort by Mean Score for a diagonal flow
q15_pci <- q15 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
  arrange(meanAnswer) %>%
  mutate(y = row_number())


q15_pci <- q15_pci %>% mutate(label = str_wrap(label, width = 30))

# 3. Generate the plot
q15_pci %>%
  ggplot(aes(y0 = y, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q15_pci$y, labels = q15_pci$label) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q15$score),
                     labels = unique(q15$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q15$respondent_id[!is.na(q15$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# 4. Save output
ggsave("./Output/q15_pci.png",
       dpi = 300,
       width = 16,
       height = 14,
       units = "cm")
```

# Question 16: How willing are you to share data for the following purposes?

```{r}
# 1. Read and process data
q16 <- read_delim("./Interim/question16.csv", 
                 delim = ";", 
                 escape_double = FALSE, 
                 trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and sort by Mean Score for a diagonal flow
q16_pci <- q16 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  mutate(pci2 = ifelse(pci2 == 0, 0.01, pci2)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
  arrange(meanAnswer) %>%
  mutate(y = row_number())

# 3. Generate the plot
q16_pci %>%
  ggplot(aes(y0 = y, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  #geom_point(aes(y = y, x = meanAnswer), alpha = 0.5) +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q16_pci$y, labels = q16_pci$label) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q16$score),
                     labels = unique(q16$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q16$respondent_id[!is.na(q16$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# 4. Save output
ggsave("./Output/q16_pci.png",
       dpi = 300,
       width = 16,
       height = 16,
       units = "cm")
```

# Question 17: How much of an issue do you consider the following obstacles to be in regards to sharing your camera trap data?

```{r}
# 1. Read and process data
q17 <- read_delim("./Interim/question17.csv", 
                  delim = ";", 
                  escape_double = FALSE, 
                  trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and sort by Mean Score for a diagonal flow
q17_pci <- q17 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
  arrange(meanAnswer) %>%
  mutate(y = row_number())

q17_pci <- q17_pci %>% mutate(label = str_wrap(label, width = 30))

# 3. Generate the plot
q17_pci %>%
  ggplot(aes(y0 = y, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q17_pci$y, labels = q17_pci$label) +
  scale_x_continuous(limits = c(-2, 2),
                     trans = "reverse", # Preserved your reversed axis transformation
                     breaks = unique(q17$score),
                     labels = unique(q17$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q17$respondent_id[!is.na(q17$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# 4. Save output
ggsave("./Output/q17_pci.png",
       dpi = 300,
       width = 16,
       height = 16,
       units = "cm")
```

# Question 18: What geographical resolution of camera trap data would you like to be shared with you?

```{r}
# 1. Read and process data
q18 <- read_delim("./Interim/question18.csv", 
                  delim = ";", 
                  escape_double = FALSE, 
                  trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and sort by Mean Score for a diagonal flow
q18_pci <- q18 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
    mutate(ord = case_when(str_detect(label, "National") ~ 7,
                         str_detect(label, "Regional") ~ 6,
                         str_detect(label, "Municipality") ~ 5,
                         str_detect(label, "Study") ~ 4,
                         str_detect(label, "Grid") ~ 3,
                         str_detect(label, "Generalised") ~ 2,
                         str_detect(label, "Exact") ~ 1
                         )
           ) %>%
  # Arranging ensures y-axis breaks and text labels line up perfectly
  arrange(ord)

# 3. Generate the plot
pl18 <- q18_pci %>%
  ggplot(aes(y0 = ord, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q18_pci$ord, labels = q18_pci$label) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q18$score),
                     labels = unique(q18$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q18$respondent_id[!is.na(q18$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# Display the plot object
pl18

# 4. Save output
ggsave("./Output/q18_pci.png",
       dpi = 300,
       width = 16,
       height = 16,
       units = "cm")
```

# Question 19: What temporal resolution of camera trap data would you like to be shared with you?

```{r}
# 1. Read and process data
q19 <- read_delim("./Interim/question19.csv", 
                  delim = ";", 
                  escape_double = FALSE, 
                  trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and apply your custom chronological sorting sequence
q19_pci <- q19 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  mutate(pci2 = ifelse(pci2 == 0, 0.01, pci2)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
  mutate(
    label = str_replace(label, "Yearly", "Annual"),
    ord = case_when(str_detect(label, "Exact") ~ 1,
                    str_detect(label, "Daily") ~ 2,
                    str_detect(label, "Weekly") ~ 3,
                    str_detect(label, "Monthly") ~ 4,
                    str_detect(label, "Annual") ~ 5)) %>%
  # Arranging ensures y-axis breaks and text labels line up perfectly
  arrange(ord) 

# 3. Generate the plot
pl19 <- q19_pci %>%
  ggplot(aes(y0 = ord, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q19_pci$ord, labels = q19_pci$label, limits = c(0.8, 5.5)) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q19$score),
                     labels = unique(q19$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q19$respondent_id[!is.na(q19$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# Display the plot object
pl19

# 4. Save output
ggsave("./Output/q19_pci.png",
       dpi = 300,
       width = 16,
       height = 12,
       units = "cm")
```

# Q13-19 together

```{r}
(pl13 + labs(title = "Share data", y = "")) + 
(pl19 + labs(title = "Receive data", y = "") + theme(axis.text.y = element_blank())) & 
  theme(plot.title = element_text(hjust = 0.5))
ggsave("./Output/q1319.png",
       dpi = 300,
       width = 16,
       height = 12,
       units = c("cm"))
```

# Q12-18 together

```{r}
(pl12 + labs(title = "Share data", y = "")) + 
(pl18 + labs(title = "Receive data", y = "") + theme(axis.text.y = element_blank())) & 
  theme(plot.title = element_text(hjust = 0.5))
ggsave("./Output/q1218.png",
       dpi = 300,
       width = 16,
       height = 14,
       units = c("cm"))
```

# Question 20: How valuable do you think data from unstructured citizen science initiatives/projects (e.g. garden projects, opportunistic camera trapping) are for the following purposes?

```{r}
# 1. Read and process data
q20 <- read_delim("./Interim/question20.csv", 
                  delim = ";", 
                  escape_double = FALSE, 
                  trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and sort by Mean Score for a diagonal flow
q20_pci <- q20 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
  arrange(meanAnswer) %>%
  mutate(y = row_number())

q20_pci <- q20_pci %>% mutate(label = str_wrap(label, width = 30))

# 3. Generate the plot
pl20 <- q20_pci %>%
  ggplot(aes(y0 = y, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q20_pci$y, labels = q20_pci$label) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q20$score),
                     labels = unique(q20$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q20$respondent_id[!is.na(q20$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# Display the plot object
pl20

# 4. Save output
ggsave("./Output/q20_pci.png",
       dpi = 300,
       width = 16,
       height = 20,
       units = "cm")
```

# Question 21: How valuable do you think data from structured citizen science (e.g. targeted camera trapping, hunter-owned camera traps) are for the following purposes?

```{r}
# 1. Read and process data
q21 <- read_delim("./Interim/question21.csv", 
                  delim = ";", 
                  escape_double = FALSE, 
                  trim_ws = TRUE) %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

# 2. Calculate PCI and sort by Mean Score for a diagonal flow
q21_pci <- q21 %>%
  group_by(charachteristic) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  ungroup() %>%
  left_join(labels, by = c("charachteristic" = "label_underscore")) %>%
  arrange(meanAnswer) %>%
  mutate(y = row_number())

q21_pci <- q21_pci %>% mutate(label = str_wrap(label, width = 30))

# 3. Generate the plot
pl21 <- q21_pci %>%
  ggplot(aes(y0 = y, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q21_pci$y, labels = q21_pci$label) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q21$score),
                     labels = unique(q21$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q21$respondent_id[!is.na(q21$response)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# Display the plot object
pl21

# 4. Save output
ggsave("./Output/q21_pci.png",
       dpi = 300,
       width = 16,
       height = 20,
       units = "cm")
```

# Q20-21 together

```{r}
(pl20 + labs(title = "Unstructured data", y = "")) + 
(pl21 + labs(title = "Structured data", y = "") + theme(axis.text.y = element_blank())) & 
  theme(plot.title = element_text(hjust = 0.5))
ggsave("./Output/q2021.png",
       dpi = 300,
       width = 16,
       height = 12,
       units = c("cm"))
```


# Question 22 + 23

```{r}
# 1. Read and combine data
q22 <- read_delim("Interim/question22.csv", 
                  delim = ";",
                  escape_double = FALSE,
                  trim_ws = TRUE) %>%
  mutate(question = "Make original images publicly available") %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

q23 <- read_delim("Interim/question23.csv", 
                  delim = ";", 
                  escape_double = FALSE, 
                  trim_ws = TRUE) %>%
  mutate(question = "Make species records publicly available (not images)") %>%
  mutate(score = as.integer(sub(".*\\((.*?)\\).*", "\\1", response))) %>%
  filter(!is.na(score))

q223 <- bind_rows(q22, q23)
remove(q22, q23)

# 2. Calculate PCI and sort by Mean Score for a diagonal flow
q223_pci <- q223 %>%
  group_by(question) %>%
  summarise(meanAnswer = mean(score), 
            sdAnswer = sd(score),
            n = n(),
            pci2 = qd_pci2(score)) %>%
  ungroup() %>%
  arrange(meanAnswer) %>%
  mutate(y = row_number())

q223_pci <- q223_pci %>% mutate(question = str_wrap(question, width = 30))

# 3. Generate the plot
q223_pci %>%
  ggplot(aes(y0 = y, x0 = meanAnswer, r = pci2, 
             fill = meanAnswer, color = meanAnswer)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_circle(alpha = 0.7) +
  
  coord_fixed() +
  scale_y_continuous(breaks = q223_pci$y, labels = q223_pci$question) +
  scale_x_continuous(limits = c(-2, 2),
                     breaks = unique(q223$score),
                     labels = unique(q223$response)) +
  
  # Professional diverging neutrality gradient (Red = Negative, Blue = Positive)
  scale_fill_gradient2(low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", midpoint = 0) +
  scale_color_gradient2(low = "#67001f", mid = "gray70", high = "#053061", midpoint = 0) +
  guides(fill = "none", color = "none") +
  
  labs(x = "",
       y = "",
       subtitle = paste0("n = ", length(unique(q223$respondent_id[!is.na(q223$score)])))) +
  
  theme_minimal() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.subtitle = element_text(hjust = 1, size = 10, color = "gray30"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 10))

# 4. Save output
ggsave("./Output/q223_pci.png",
       dpi = 300,
       width = 16,
       height = 8,
       units = "cm")
```

